---
title: "Mapping and Spatial Analysis in R!"
subtitle: "Part 3-Interaction, Animation, etc."
author: "Kevin Stierhoff <br /> <br /> NOAA Fisheries <br /> Southwest Fisheries Science Center"
date: '`r format(Sys.time(), format = "%F")`'
output:
  xaringan::moon_reader:
    css: ["default","css/css-slides.css"]
    lib_dir: libs
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
# Install and load pacman (library management package)
if (!require("pacman")) install.packages("pacman")

# Install and load required packages from CRAN ----
pacman::p_load(xaringan,knitr,here,emo,leaflet,mapview,
               gganimate,sf,dplyr,ggplot2, install = FALSE)

pacman::p_load_gh("hadley/emo", install = FALSE)

options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(message = F, fig.align = 'center',
                      fig.dim = c(6.5, 6.1), fig.retina = 2, 
                      out.height = "100%")
knitr::opts_hooks$set(fig.callout = function(options) {
  if (options$fig.callout) {
    options$echo <- FALSE
    options$out.height <- "99%"
    options$fig.width <- 16
    options$fig.height <- 8
  }
  options
})
```

## `Leaflet` for Interactive Maps

[Leaflet](https://rstudio.github.io/leaflet/) is one of the most popular open-source JavaScript libraries for interactive maps. This R package makes it easy to integrate and control Leaflet maps in R.

```{r,out.width='8in',out.height='70%',out.width='100%'}
# The SWFSC
leaflet() %>% addTiles() %>% addProviderTiles(providers$Esri.OceanBasemap) %>% setView(-117.2512, 32.8707, zoom = 17)
```  

[Leaflet Provider Tile Gallery](http://leaflet-extras.github.io/leaflet-providers/preview/index.html)

---

## `gganimate` for Animated Maps

[gganimate](https://gganimate.com/) is an extremely powerful and (mostly) simple package for making animated `ggplot2` maps.

---

## `rayshader` for 3D visualization

The [rayshader](https://www.rayshader.com/) package is a brand new and quite amazing package for visualizing and animating data in 3D and 4D. 
 

